---
title: "Coursework"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
data=read.csv('Cwk_rectime_20363451.csv')
```

#Part 1
*Task 1:Calculate the sample size required to reject the null hypothesis H0: µ = 148 in favour of the alternative hypothesis H1: µ = 142 with significance level 10% and power 90%.*

```{r}
mu=6
sigma=41
alpha=0.1
power=0.9
n=((qnorm(1-alpha)-qnorm(1-power))*sigma/mu)^2
print(n)
```

#Part 2
*Task 2:Construct a 99% confidence interval for µ. Describe how the confidence interval is constructed.*
```{r}
x1=mean(data$Recovery.time)-qt(0.995,df=length(data$Recovery.time)-1)*sd(data$Recovery.time)/sqrt(length(data$Recovery.time))
x2=mean(data$Recovery.time)+qt(0.995,df=length(data$Recovery.time)-1)*sd(data$Recovery.time)/sqrt(length(data$Recovery.time))
print(c(x1,x2))
```

```{r}
t.test(data$Recovery.time,mu=148,conf.level = 0.99,alternative = 'greater')
```
```{r}
t.test(data$Recovery.time,mu=148,conf.level = 0.99,alternative = 'less')
```



#Part 3
```{r}
data=read.csv('Cwk_data_20363451.csv')
```

*Task 3:Create a covariate bmi.  The bmi of a patient is given by (weight in kg)/(height in m)^2.             There are four main categories of bmi underweight (< 18.5), healthy (18.5 − 25), overweight (25 − 30) and obese (> 30). Is the bmi category of a patient receiving Vunder independent of hospital?*
```{r}
head(data)
```
```{r}
data$bmi=(data$weight)/(data$height/100)^2
```

Now look at the bmi.
```{r}
head(data)
```


```{r}
len=length(data$bmi)
for (i in 1:len){
  if (data[i,]$bmi<18.5){
    data$bmi_category[i]=1
  }else if (data[i,]$bmi>=18.5 & data[i,]$bmi<25){
    data$bmi_category[i]=2
  }else if (data[i,]$bmi>=25 & data[i,]$bmi<30){
    data$bmi_category[i]=3
  }else{
    data$bmi_category[i]=4
  }
}
```

Now look at bmi_category.
```{r}
head(data)
```
```{r}
table(data$hospital,data$bmi_category)
```

Now test for independence.
```{r}
chisq.test(table(data$hospital,data$bmi_category))
```
*Task 4:Find the most appropriate linear regression model for predicting the recovery time after surgery, y, in terms of the covariates provided, including bmi.*

```{r}
data=read.csv("Cwk_data_20363451.csv")
data$bmi=(data$weight)/(data$height/100)^2
head(data)
```

```{r}
model=lm(Recovery.time~.,data=data)
bestmodel=step(model)
summary(bestmodel)
```
smoker=1,hospital=3,age=59,height=177,weight=99.1
```{r}
bmi=99.1/1.77^2
pred=predict(bestmodel,newdata = data.frame(smoker=1,hospital=3,bmi=bmi),interval = "prediction")
pred
```

